### 2021-04-13 sections/model_overview/main.tex
Apply minor changes and fix typos

% PAR: GENERAL
% Intro
The problem studied is a 3-player game theoretic scenario between two queueing 
systems and a service that distributes individuals to them. 
% General objectives of players
Each player in this game has its own objectives and cares about meeting its own 
targets.
% Specific objectives
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals need to spend in the system, 
while the distribution service aims to minimise the time that its individuals 
are blocked.

% PAR: OBJECTIVES OF QUEUEING SYSTEMS
% Intro
The queueing systems are designed in such a way where they can accept two types
of individuals. 
These are the individuals that the distribution service allocates to them and 
other individuals from other sources. 
% Specific Formulation
Each queueing system may then choose to block the individuals that arrive from 
the service distribution when the system reaches a certain capacity. 
Thus, the set of strategies that they may choose to play in the game are defined 
as the set of possible choices that the two queueing systems have. 
In other words, each queueing system is given \( N_A \) and \( N_B \) number of 
strategies where \( N_A \) and \( N_B \) are the total capacities of the two 
queueing systems.
The \textit{threshold} parameter is thus used to capture the chosen 
strategy for each hospital where \( T_A \in \left[1, N_A \right] \) and 
\( T_B \in \left[1, N_B \right] \)
% Specific Objectives
Their choice of strategy will then rely solely on satisfying their own 
objective, which is to make sure that the waiting time of a proportion of 
individuals will be below the predefined target time.

@@

% PAR: OBJECTIVES OF DISTRIBUTION SERVICE
% Intro
On the other side of the spectrum, the service distribution has its own choices 
to make and its own goals to satisfy.
% Specific Formulation
The set of strategies it has can be defined as the different ways that it can 
distribute individuals to the two queueing system.
Therefore, unlike the queueing systems, the distribution service has a 
continuous set of strategies that goes from \( 0\% - 100\% \). 
For example, it may choose to send \(35\%\) of its individuals to the first 
queueing system and \(65\%\) to the second one.
% Specific Objectives
In addition, the distribution services aims to minimise any potential blockages
that may occur give the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distribution service is the proportion of lost individuals.
Equation \ref{eq:obj-distribution-service} can be used to capture a mixture 
between the two objectives.
systems.

>>>>

The problem studied is a 3-player game theoretic scenario between two queueing 
systems and a service that distributes individuals to them. 
Each player in this game has its own objectives and cares about meeting its own 
targets.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals need to spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.

The queueing systems are designed in such a way where they can accept two types
of individuals. 
These are the individuals that the distributor allocates to them and 
other individuals from other sources. 
Each queueing system may then choose to block the individuals that arrive from 
the distributor when the system reaches a certain capacity. 
Thus, the set of strategies that they may choose to play in the game are defined 
as the set of possible choices that the two queueing systems have. 
In other words, each queueing system is given \( N_A \) and \( N_B \) number of 
strategies where \( N_A \) and \( N_B \) are the total capacities of the two 
queueing systems.
The \textit{threshold} parameter is thus used to capture the chosen 
strategy for each hospital where \( T_A \in \left[1, N_A \right] \) and 
\( T_B \in \left[1, N_B \right] \)
Their choice of strategy will then rely solely on satisfying their own 
objective, which is to make sure that the waiting time of a proportion of 
individuals will be below the predefined target time.

@@

On the other side of the spectrum, the distributor has its own choices 
to make and its own goals to satisfy.
The set of strategies it has can be defined as the different ways that it can 
distribute individuals to the two queueing system.
Therefore, unlike the queueing systems, the distributor has a 
continuous set of strategies that goes from \( 0\% - 100\% \). 
For example, it may choose to send \(35\%\) of its individuals to the first 
queueing system and \(65\%\) to the second one.
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distribution service is the proportion of lost individuals.
Equation \ref{eq:obj-distribution-service} can be used to capture a mixture 
between the two objectives.
